---
title: "Getting Started with urogynScorer"
author: "Tyler Muffly, MD"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with urogynScorer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

## Introduction

The `urogynScorer` package provides tools for scoring standardized questionnaires used in urogynecology and pelvic floor medicine. This vignette serves as a general introduction and demonstrates the basic usage of the package's primary functions.

```{r setup}
library(urogynScorer)
library(dplyr)
```

## Key Features

- Standardized scoring of validated urogynecology questionnaires
- Robust validation of input data
- Detailed logging capabilities
- Consistent handling of missing values
- Support for multiple column naming conventions

## Available Instruments

The package currently supports scoring for the following instruments:

1. **Pelvic Floor Distress Inventory (PFDI-20)** - Including its subscales:
   - Pelvic Organ Prolapse Distress Inventory (POPDI-6)
   - Colorectal-Anal Distress Inventory (CRADI-8)
   - Urinary Distress Inventory (UDI-6)
2. **Patient Global Impression of Improvement (PGI-I)**
3. **Sandvik Severity Index** for urinary incontinence

## Example 1: Scoring the PFDI-20

The PFDI-20 measures pelvic floor symptoms across three domains. Let's look at an example of scoring this questionnaire:

```{r pfdi-example}
# Load the sample PFDI data included with the package
data("pfdi_data_minimal")

# Examine the structure of the data
str(pfdi_data_minimal)

# Calculate PFDI-20 scores
pfdi_results <- calculate_pfdi_scores(
  input_data = pfdi_data_minimal,
  id_column = "Record_ID",
  missing_threshold = 0.5,  # Allow up to 50% missing values per subscale
  verbose = FALSE
)

# View the first few results
head(pfdi_results)
```

## Example 2: Scoring the PGI-I

The Patient Global Impression of Improvement (PGI-I) scale measures subjective improvement following treatment:

```{r pgii-example}
# Create sample PGI-I data
pgii_data <- data.frame(
  Record_ID = c("PT001", "PT002", "PT003", "PT004", "PT005"),
  pgii_response = c(1, 2, 3, 4, NA)  # 1=Very much better, 7=Very much worse
)

# Score PGI-I responses
pgii_results <- score_pgii(
  patient_data = pgii_data,
  item_name = "pgii_response",
  keep_n_valid = TRUE,
  verbose = FALSE
)

# View results
pgii_results
```

## Example 3: Calculating Sandvik Severity Index

The Sandvik Severity Index measures urinary incontinence severity:

```{r sandvik-example}
# Create sample frequency and amount data
frequency <- c(0, 1, 2, 3, 4)  # 0=Never to 4=Daily
amount <- c(1, 2, 3, 2, 1)     # 1=Drops to 3=Large amounts

# Calculate Sandvik Severity Index
sandvik_results <- sandvik_severity_index(frequency, amount)

# View results
sandvik_results
```

## Working with Your Own Data

When working with your own data, you'll need to ensure the column names match the expected format or use the appropriate parameters to specify your column names.

### Tips for PFDI-20 Scoring

The `calculate_pfdi_scores()` function supports several column naming conventions, including:

- Standard format: `popdi_q*`, `cradi_q*`, `udi_q*`
- Numeric format: `PFDI-1` through `PFDI-20`
- Subscale-specific format: `PFDI-POPDI-*`, `PFDI-CRADI-*`, `PFDI-UDI-*`
- Dot notation: `PFDI.1`, `PFDI.2`, etc.

### Tips for PGI-I Scoring

The PGI-I responses must be integers between 1 and 7, where:
- 1: Very much better
- 2: Much better
- 3: A little better
- 4: No change
- 5: A little worse
- 6: Much worse
- 7: Very much worse

The `score_pgii()` function adds a binary improvement indicator (1 = improved [1-3], 0 = not improved [4-7]).

## Conclusion

The `urogynScorer` package provides a standardized approach to scoring common urogynecology questionnaires, ensuring consistent and reproducible results in both research and clinical applications.

For more detailed information on each scoring function, please see the dedicated vignettes or the function documentation.
